Supporting Non-Functional Requirements for Services Software Process: An MDD Approach

### 2013-10-15 SOFSEM2014/FinalVersion/main.tex
Ack -- martin

\section{Introduction}
\label{sec:intro}
\include{introduction}

\section{SOD-M}\label{sec:sodm}
\include{sodm}

\section{$\pi$SOD-M}\label{sec:pisodm}
\include{pisodm}

\section{Proof of Concept: \textit{Tracking Crimes}}\label{sec:poc}
\include{proofOfConcept}

\section{Related Work and Conclusions}
\label{sec:conclusions}
\include{conclusion}

>>>>

\section{Introduction}
\label{sec:intro}
\input{introduction}

\section{SOD-M}\label{sec:sodm}
\input{sodm}

\section{$\pi$SOD-M}\label{sec:pisodm}
\input{pisodm}

\section{Proof of Concept: \textit{Tracking Crimes}}\label{sec:poc}
\input{proofOfConcept}

\section{Related Work and Conclusions}
\label{sec:conclusions}
\input{conclusion}

\section*{Acknowledgements}
This work was partly supported by the National Institute of Science and Technology for Software Engineering (INES\footnote{www.ines.org.br}), funded by CNPq (Brazil), grants 573964/2008-4 and 305619/2012-8; CAPES/UdelaR (Brazil/Uruguay) grant 021/2010; CAPES/STIC-AmSud (Brazil) grant 020/2010).
